Titeln på avhandlingens språk

### 2023-01-17 body/part1/overview/extending-wca.tex
wrap

\section{Extending the methodology in the context of \gls{WCA}}

@@

\todo[inline]{Discuss implications?}

@@

@@

\todo[inline]{Probably needs to repeat a discussion on why the new model is necessary.
This discussion should first be presented at the beginning of this section however.}

@@

\subsubsection{Procedural generation of dynamic traces of video frames for \gls{WCA}}\label{model:traces}

>>>>

\section{Extending the methodology in the context of \acs{WCA}}\label{sec:extendingmethodology}

@@

@@

\subsubsection{Implications}

The results summarized above lead to interesting implications for the design and optimization of \gls{WCA} application systems.
The behavioral slow-down in users as a response to reductions in system responsiveness translates into noticeably extended application lifetimes, even for short durations of impairment.
Combined with the permanence of these effects for a period even after the system returns to an improved level of responsiveness, this could lead to unconventional consequences for resource allocation, in particular in multi-tenant deployment and in cases where a user may be able to finish the task before the effects of slow-down subside.
In such cases, it might be more efficient to not divert resources to the impaired application, as fair degradation may not ultimately be beneficial to the system as a whole.
It might even be more beneficial to divert resources \emph{away} from the impaired application, to ensure optimal system responsiveness for other tenants in the system.

These implications, however, are merely speculative.
Moreover and as previously discussed, due to the complexity of these systems, accurate study of the actual consequences of the results discussed in the present section can only be achieved through an experimental approach.
\todo[inline]{Does this need a better transition?}

@@

\todo[inline]{Probably needs to repeat a discussion on why the new model is necessary, in a shorter summarized form.
This discussion should first be presented at the beginning of this section however.}

@@

\subsubsection{Procedural generation of dynamic traces of video frames for \acs{WCA}}\label{model:traces}

### 2023-01-17 body/part1/overview/implications-optimization.tex
wrap

\section{Implications for the optimization of \gls{WCA}}

>>>>

\section{Implications for the optimization of \acs{WCA}}

In this section, we will discuss the implications of the methodology for the optimization of \gls{WCA} applications, in particular when employing the experimental results and the improved model of human timings discussed in \cref{sec:extendingmethodology}.
The version of this discussion presented here is a summarized version of what \cref{paper:olguinmunoz2023realistic} exposes.

\todo[inline]{Do we need more experiments?}

\subsection{Implications with respect to application lifetime footprints}

\subsection{Implications with respect to number of samples per step}

\subsection{Implications with respect to raw energy consumption}
